### 2017-04-29 paper/jfp-submission/abstract.tex
mention localization in abs/intro

\begin{abstract}
  %
  {Static} type errors are a common stumbling block
  for newcomers to typed functional languages.
  %
  We present a {dynamic} approach to explaining type
  errors by generating counterexample witness inputs that
  illustrate how an ill-typed program goes wrong.
  %
  First, given an ill-typed function, we symbolically
  execute the body to synthesize witness values that
  make the program go wrong.
  We prove that our procedure synthesizes
  {general} witnesses in that if a witness is
  found, then for all inhabited input types,
  there exist values that can make the function go wrong.
  %
  Second, we show how to extend the above procedure to
  produce a reduction graph that can be used to
  interactively visualize and debug witness executions.
  %
  Third, we evaluate the coverage of our approach
  on two data sets comprising over 4,500 ill-typed
  student programs.
  Our technique is able to generate witnesses for
  88\% of the programs, and our reduction graph
  yields small counterexamples for 81\% of the witnesses.
  %
  Finally, we evaluate whether our witnesses help
  students understand and fix type errors, and
  find that students presented with our witnesses
  show a greater understanding of type errors
  than those presented with a standard error message.
\end{abstract}

>>>>

\begin{abstract}
  %
  {Static} type errors are a common stumbling block
  for newcomers to typed functional languages.
  %
  We present a {dynamic} approach to explaining type
  errors by generating counterexample witness inputs that
  illustrate how an ill-typed program goes wrong.
  %
  First, given an ill-typed function, we symbolically
  execute the body to synthesize witness values that
  make the program go wrong.
  We prove that our procedure synthesizes
  {general} witnesses in that if a witness is
  found, then for all inhabited input types,
  there exist values that can make the function go wrong.
  %
  Second, we show how to extend the above procedure to
  produce a reduction graph that can be used to
  interactively visualize and debug witness executions.
  %
  Third, we evaluate the coverage of our approach
  on two data sets comprising over 4,500 ill-typed
  student programs.
  %
  Our technique is able to generate witnesses for
  around 85\% of the programs, our reduction graph
  yields small counterexamples for over 80\% of the witnesses,
  and a simple heuristic allows us to use witnesses to
  locate the source of type errors with around 70\% accuracy.
  %
  Finally, we evaluate whether our witnesses help
  students understand and fix type errors, and
  find that students presented with our witnesses
  show a greater understanding of type errors
  than those presented with a standard error message.
\end{abstract}

### 2017-04-29 paper/jfp-submission/evaluation.tex
mention localization in abs/intro

In the sequel we present our experimental methodology (\S~\ref{sec:methodology})
and then answer the above questions.
%
However, for the impatient reader, we begin with a quick summary of our main results:

\paragraph{1. Most Type Errors Admit Witnesses}
Our prime result is that the vast majority of static type errors, around
85\%, do in fact admit a dynamic witness.
%
Further, \toolname efficiently synthesizes witnesses with its randomized search;
it can synthesize a witness for over 75\% of programs in under one second, \ie
fast enough to be integrated into the edit-compile-debug cycle.
%

@@

\paragraph{4. Witnesses Assign Blame}
Finally, we find that a simple heuristic allows us to use witnesses
to \emph{automatically} assign blame for type errors.
%
We treat the values inside the stuck term as \emph{sources} of typing
constraints and the stuck term itself as a \emph{sink}, producing
a small slice of the program that likely contains the error.
%
Using this heuristic, \toolname's witness are competitive with the
state-of-the-art type error localization tools \mycroft and \sherrloc.

>>>>

In the sequel we present our experimental methodology (\S~\ref{sec:methodology})
and then answer the above questions.
%
However, for the impatient reader, we first summarize our main results:

\paragraph{1. Most Type Errors Admit Witnesses}
Our prime result is that the vast majority of static type errors, around
85\%, do in fact admit a dynamic witness.
%
Further, \toolname efficiently synthesizes witnesses with its randomized search;
it can synthesize a witness for over 75\% of programs in under one second, \ie
fast enough for interactive use. %to be integrated into the edit-compile-debug cycle.
%

@@

\paragraph{4. Witnesses Assign Blame}
Finally, we present a simple heuristic that allows us to use witnesses
to \emph{automatically} assign blame for type errors.
%
We treat the values inside the stuck term as \emph{sources} of typing
constraints and the stuck term itself as a \emph{sink}, producing
a slice of the program that likely contains the error.
%
Using this heuristic, \toolname's witness are competitive with the
state-of-the-art localization tools \mycroft and \sherrloc.
